BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-07-11 Paper/BOAST.tex
bugfix
WIP paper with JFM.

%% or include affiliations in footnotes:
\author[mymainaddress]{Brice Videau}
\ead{brice.videau@imag.fr}

@@

\begin{keyword}
Code Generation \sep Portability \sep High Performance Computing \sep
Autotuning \sep Non Regression Testing
\end{keyword}

@@

Porting and tuning HPC applications to new platforms is tedious and costly
in term of human resources. Portability efforts are often lost when
migrating to a new architecture, or code lose maintainability because
several versions of the code coexist, usually with a lot of duplication.
Thus productivity of porting and tuning efforts is low as a huge fraction
of those developments are never used after the platform they were intended
for is decommissioned.

@@

Evolution of HPC Architectures is rapid and also diverse: in the last 5
years no less than 6 architectures have been number one in the Top500:
\begin{itemize}
\item Intel Processor + Xeon Phi (Tianhe-2)
\item AMD Processor + NVIDIA GPU (Titan)
\item IBM BlueGene/Q (Sequoia)
\item Fujitsu SPARC64 (K computer)
\item Intel Processor + NVIDIA GPU (Tianhe-1)
\item AMD Processor (Jaguar)
\end{itemize}
Being able to efficiently use those architectures on such a small
time-frame is challenging.

@@

  \subsection{HPC Applications}

@@

@@

  \subsection{BOAST Runtime}
     + dumper pour tests de non régression

@@

@@

>>>>

%% or include affiliations in footnotes:
\author[mymainaddress]{Brice Videau}
\ead{brice.videau@imag.fr}
\author{Kevin Pouget}
\author{Luigi Genovese}
\author{Thierry Deutsch}
\author{Dimitri Komatitsch}
\author{Jean-François Méhaut}

@@

\begin{keyword}
Code Generation \sep Portability \sep Genericity \sep Productivity and Software
Design \sep High Performance Computing \sep Autotuning \sep Non Regression
Testing
\end{keyword}

@@

Porting and tuning HPC applications to new platforms is tedious and costly
in term of human resources.

Portability efforts are often lost when
migrating to a new architecture, or code lose maintainability because
several versions of the code coexist, usually with a lot of duplication.

Thus productivity of porting and tuning efforts is low as a huge fraction
of those developments are never used after the platform they were intended
for is decommissioned.

Généricité
 et
fonctionalités

@@

Evolution of HPC Architectures is rapid and also diverse: in the last 5
years no less than 6 architectures have been number one in the Top500:
\begin{itemize}
\item Intel Processor + Xeon Phi (Tianhe-2)
\item AMD Processor + NVIDIA GPU (Titan)
\item IBM BlueGene/Q (Sequoia)
\item Fujitsu SPARC64 (K computer)
\item Intel Processor + NVIDIA GPU (Tianhe-1)
\item AMD Processor (Jaguar)
\end{itemize}
Being able to efficiently use those architectures on such a small
time-frame is challenging. Stress frequency of architecture changes.

@@

transition architecture application

  \subsection{Scientific Computing Applications}

@@

Ajouter Multiplicité des devs et donc problèmatique de maintenabilité ++

@@

  \begin{itemize}
  \item Abstraction of programming concepts: variables, procedures
  \item Operator overloading: simpler syntax
  \item Two languages in one
  \end{itemize}

  \subsection{BOAST Runtime}

   multitarget generation
   compilation
   execution
  + dumper et replay pour tests de non régression

@@

    \subsubsection{A Generic Convolution Library}

  characteristique use case driven

  bibliotheque premier pas vers un dsl

@@

    \subsubsection{Porting to OpenCL}
